Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-23 manuscript.Rmd
Fixed error in label.

ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.80, colour = "black", size = .2) + 
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)),
        labels = c("Systematic review", "RCT", "Cohort/Case Control", 
           "Meta-analysis")) +
  ylim(c(0, 60)) + 
    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1), 
          panel.grid.minor=element_blank(),
         legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Frequency") + 
    xlab("Year") + 
    labs(fill = "Study type") + 
    scale_y_continuous(breaks = seq(0,60, 10))

>>>>

ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.80, colour = "black", size = .2) + 
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)),
        labels = c("Systematic review", "RCT", "Quasi-experimental", 
           "Meta-analysis")) +
  ylim(c(0, 60)) + 
    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1), 
          panel.grid.minor=element_blank(),
         legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Frequency") + 
    xlab("Year") + 
    labs(fill = "Study type") + 
    scale_y_continuous(breaks = seq(0,60, 10))
